Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-06 03-interest-flooding.tex
small changes
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@866 df1a90cd-247b-4364-bdaf-287a704eb499

\paragraph{Classification}

@@

The Interest flooding attack has two-fold effect on service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.

>>>>

% \paragraph{Classification}

@@

The Interest flooding attack has two main mechanisms to affect service quality in NDN network: it \emph{creates network congestion} and \emph{exhaust resources on routers}.
